### 2019-05-24 doc/chapters/towards_verifying.tex
propagate require

>>>>

\subsection{Propagate require}
Finally the code works with Stainless.
But there is another problem.
Bitcoin-S-Core uses require like a fail-fast method where as Stainless needs it to verify the code.

Stainless output:
\begin{lstlisting}
  [Warning ] Found counter-example:
  [Warning ]   thiss: { x: Object | @unchecked isNumber(x) } -> Int64Impl(0)
  [Warning ]   num: { x: Object | @unchecked isInt64(x) }    -> 
                 Int64Impl(9223372036854775808)
\end{lstlisting}
Corresponding code:
\begin{lstlisting}
  sealed abstract class Number extends BasicArithmetic[Int64] {
    override def +(num: Int64): Int64 = apply(checkResult(underlying + num.underlying))

    private def checkResult(result: BigInt): BigInt = {
      require(
        result <= BigInt("9223372036854775807")
        && result >= BigInt("-9223372036854775808")
      )
      result
    }
  }
\end{lstlisting}
But how can Stainless find a counter example ignoring the require in checkResult?
Since Stainless is a static verification tool, it tests every possibility.
So it can use a number bigger than the maximum Int64 and pass it to the addition.
The require in checkResult will then fail.
Thus, the addition need to have the restrictions of checkResult too.
\begin{lstlisting}
  override def +(num: Int64): Int64 = {
    require(
      num.underlying <= BigInt("9223372036854775807")
      && num.underlying >= BigInt("-9223372036854775808")
      && this.underlying <= BigInt("9223372036854775807")
      && this.underlying >= BigInt("-9223372036854775808")
    )
    apply(checkResult(underlying + num.underlying))
  }
\end{lstlisting}
Stainless finds another counter example:
\begin{lstlisting}
  [Warning ] Found counter-example:
  [Warning ]   num: { x: Object | @unchecked isInt64(x) }    -> Int64Impl(1)
  [Warning ]   thiss: { x: Object | @unchecked isNumber(x) } ->
                 Int64Impl(9223372036854775807)
\end{lstlisting}
Sure, it can just add one to the maximum Int64 and the require does not hold anymore.
The goal is to check the addition of zero so lets add a restriction for num to be zero.

Finally, it works and verifies correctly.
